Staged Abstract Interpreters

### 2019-09-11 paper/70_eval.tex
typo
misc

We use Scala 2.12.8 and Oracle JVM 1.8.0-191 \footnote{The options for
running the JVM are set to the following: \texttt{-Xms2G -Xmx8G -Xss1024M
-XX:MaxMetaspaceSize=2G - XX:ReservedCodeCacheSize=2048M}},
running on an Ubuntu 16.04 LTS (kernel 4.4.0) machine. All our
evaluations were performed on a machine with 4 Intel Xeon Platinum
8168 CPU at 2.7GHz and 3 TB of RAM. Although the machine has 96 cores
(192 threads) in total, the abstract interpreters are single-threaded.
To minimize the effect of warm-up from the HotSpot JIT compiler,
all the experiments are executed for 20 times and we report the
statistical median value of the running times. We set a 5 minute
timeout.

@@

Figure~\ref{evaluation_result} shows the evaluation result, comparing the
performance improved by staging on the two monovariant CFAs. The
\textit{unstaged} and \textit{staged} columns show the median time (excluding
pre-compilation) to finish the analysis. The column
$\frac{\text{unstaged}}{\text{staged}}$ shows the improvement. The dash @-@ in
some cells indicates timeout.  As expected, the staged version significantly
outperforms the unstaged version on all benchmarks.
%We observe that simple value domains used in the benchmark usually leads to
%better speed-ups, for example, the @kcfa-worst@ series only uses lambdas and
%booleans.
For 0CFA without store-widening, we observe an average speedup of ~17x times;
for 0CFA with store-widening, the average speedup is ~7x times.
\texttt{kcfa-worst-64} has the highest speedup among all the tests. Although it
has a comparably large size of AST, it has a rather simple structure which only
involves booleans, lambda terms, and applications. We conjecture that the simple
domain and structure allow the generated code to be efficiently optimized by the
JVM. However, on the corresponding 0CFA-SW, we do not observe such a significant
speedup. Due to the complexity of generated code and next-stage running platform
(JVM), we leave the detailed empirical analysis of which static analysis can
benefit more from the specialization as future work.

>>>>

We use Scala 2.12.8 and Oracle JVM 1.8.0-191 \footnote{The options for
running the JVM are set to the following: \texttt{-Xms2G -Xmx8G -Xss1024M
-XX:MaxMetaspaceSize=2G - XX:ReservedCodeCacheSize=2048M}},
running on an Ubuntu 16.04 LTS (kernel 4.4.0) machine. All our
evaluations were performed on a machine with 4 Intel Xeon Platinum
8168 CPUs at 2.7GHz and 3 TB of RAM. Although the machine has 96 cores
(192 threads) in total, the abstract interpreters are single-threaded.
To minimize the effect of warm-up from the HotSpot JIT compiler,
all the experiments are executed for 20 times and we report the
statistical median value of the running times. We set a 5 minute
timeout.

@@

Figure~\ref{evaluation_result} shows the evaluation result, comparing the
performance improved by staging on the two monovariant CFAs. The
\textit{unstaged} and \textit{staged} columns show the median time (excluding
pre-compilation) to finish the analysis. The column
$\frac{\text{unstaged}}{\text{staged}}$ shows the improvement. The dash @-@ in
some cells indicates timeout.  As expected, the staged version significantly
outperforms the unstaged version on all benchmarks.
%We observe that simple value domains used in the benchmark usually leads to
%better speed-ups, for example, the @kcfa-worst@ series only uses lambdas and
%booleans.
For 0CFA without store-widening, we observe an average speedup of ~17 times;
for 0CFA with store-widening, the average speedup is ~7 times.
\texttt{kcfa-worst-64} has the highest speedup among all the tests. Although it
has a comparably large size of AST, it has a rather simple structure which only
involves booleans, lambda terms, and applications. We conjecture that the simple
domain and structure allow the generated code to be efficiently optimized by the
JVM. However, on the corresponding 0CFA-SW, we do not observe such a significant
speedup. Due to the complexity of generated code and next-stage running platform
(JVM), we leave the detailed empirical analysis of which static analysis can
benefit more from the specialization as future work.
